---
title: "parent"
author: "R. Mark Sharp"
date: "4/2/2021"
output: 
  bookdown::pdf_document2:
    keep_tex: true
    number_sections: true
linkcolor: blue
urlcolor: red
citecolor: green
toc: true

---

```{r setup, include=FALSE}
library(kableExtra) # for kbl() function
library(stringi)
knitr::opts_chunk$set(echo = TRUE, include = TRUE, results = "rmarkdown")

```


# Reference Examples

Notice the top level YAML header color settings for the various links.

[This section](#rmarkdown-2) should take you to **RMarkdown 2** in _child_2.Rmd

You can also link to specific text such as the 
[knitr description](#knitr-description).

You can embed plots and reference them with the \\@ref(label) syntax, which
provides the number of the item being referenced. For example, see 
Figure \@ref(fig:pressure) below.

You can embed tables and reference them. For example, see Table
\@ref(tab:cars-fivenum) below.

Tables and Figures are automatically numbered in their individual sequences. 

Note that though there are multiple tables and figures, only those with 
captions get labels created that can be used for references.


```{r pressure, fig.cap = "Temperature vs Pressure", echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```{r child = "children/_child_1.Rmd", ref = "child-1"}
```

Child 2 file is next.

```{r child = "children/_child_2.Rmd", ref = "child-2"}
```

